How to obtain the redshift distribution from probabilistic redshift estimates

### 2017-06-15 research/paper/draft.tex
adding figures to paper

\begin{enumerate}
	\item Choose a true $n(z)$ that is a continuous function with known 
parameters $\vec{\theta}$.
	\item Sample the true $n(z)$ to create a catalog of $N$ true redshifts 
$z_{i}$.
	\item Choose a true intrinsic scatter $\sigma$, and sample Gaussians 
$p(z'_{i} | z_{i}, \sigma) = \mathcal{N}(z_{i}, \sigma)$ to get "observed" 
redshifts $z'_{i}$ defining Gaussian likelihoods $p(\vec{d}_{i} | z'_{i}, 
\sigma) = \mathcal{N}(z'_{i}, \sigma)$.
	\item Choose a parametrization and the parameters $\vec{\phi}^{*}$ of 
the interim prior.
	\item Create interim posteriors $p(z_{i} | \vec{d}_{i}, \vec{\phi}^{*}) 
= p(\vec{d}_{i} | z_{i})\ p(z_{i} | \vec{\phi}^{*})$ in this parametrization.
\end{enumerate}

This method for deriving mock data is referred to as the fiducial case, and 
variations on it will refer directly to the steps that are altered.

@@

Existing $n(z)$ estimators are systematically smoother than the true $n(z)$.  
Here we show that the traditional estimators of $n(z)$ cannot recover a highly 
featured $n(z)$.  The implication of this failure is quite serious; the 
consistently smooth, unimodal $n(z)$ estimates appearing in the literature 
could result from much more featured true redshift distributions, and there 
would be no way to catch this error without using a fully probabilistic method.

@@

\includegraphics[width=0.5\textwidth]{fig/fiducial/estimators.png}		
		\caption{[plot of a highly featured, multimodal true $n(z)$]}
		\label{fig:featured}
	\end{center}
\end{figure}

@@

In the following test cases, we vary the properties of the mock photo-$z$ 
likelihoods in an effort to emulate known systematics in photo-$z$ estimation.

@@

\begin{figure}
	\begin{center}
		%\includegraphics[width=0.5\textwidth]{pgm.png}
		\caption{[plot of $z_{phot}$ vs. $z_{spec}$ with varying 
intrinsic scatter]}
		\label{fig:intscat}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
		%\includegraphics[width=0.5\textwidth]{pgm.png}
		\caption{[plot of $z_{phot}$ vs. $z_{spec}$ with template-like 
catastrophic outliers]}
		\label{fig:tempcatout}
	\end{center}
\end{figure}

@@

Existing $n(z)$ estimation routines will always produce a biased estimator when 
the interim prior is not equal to the true $n(z)$.  We demonstrate here that 
regardless of the appropriateness of the interim prior as an approximation to 
the true $n(z)$, \chippr is not affected by the choice of the interim prior so 
long as it has nontrivial coverage in the space of redshift.

>>>>

\begin{enumerate}
	\item \label{itm:true} Choose a true $n(z)$ that is a continuous 
function with known parameters $\vec{\theta}$.
	\item \label{itm:sample} Sample the true $n(z)$ to create a catalog of 
$N$ true redshifts $z_{i}$.
	\item \label{itm:scatter} Choose a true intrinsic scatter $\sigma$, and 
sample Gaussians $p(z'_{i} | z_{i}, \sigma) = \mathcal{N}(z_{i}, \sigma)$ to 
get "observed" redshifts $z'_{i}$ defining Gaussian likelihoods $p(\vec{d}_{i} 
| z'_{i}, \sigma) = \mathcal{N}(z'_{i}, \sigma)$.
	\item \label{itm:interim} Choose a parametrization and the parameters 
$\vec{\phi}^{*}$ of the interim prior.
	\item \label{itm:posterior} Create interim posteriors $p(z_{i} | 
\vec{d}_{i}, \vec{\phi}^{*}) = p(\vec{d}_{i} | z_{i})\ p(z_{i} | 
\vec{\phi}^{*})$ in this parametrization.
\end{enumerate}

In all of the following validation tests, we use $10$ bins and $N = 10,000$ 
galaxies.  In Secs. \ref{sec:truth} and \ref{sec:likelihoods}, we use a flat 
interim prior.  This method for deriving mock data is referred to as the 
fiducial case, and variations on it will refer directly to the steps that are 
altered.

@@

Existing $n(z)$ estimators are systematically smoother than the true $n(z)$.  
Here we show that the traditional estimators perform better when the true 
$n(z)$ is weakly featured than when the true $n(z)$ is strongly featured by 
experimenting with Step \ref{itm:true} of Sec. \ref{sec:mockdata}.  The 
implication of this issue is quite serious; the consistently smooth, unimodal 
$n(z)$ estimates appearing in the literature could result from much more 
featured true redshift distributions, and there would be no way to catch this 
error without using a fully probabilistic method.

@@

\includegraphics[width=0.5\textwidth]{fig/fiducial/estimators.png}		
		\caption{[This plot doesn't really show what I want because the 
intrinsic scatter is too low!  I used $\sigma=0.03$ because that's what has 
been quoted as what LSST, etc. needs, but that's not what comes out of 
photo-$z$ estimation methods before they impose aggressive cuts.]  Top panel: 
The traditional MAP reduction of a photo-$z$ PDF against the true redshifts 
with a few rescaled photo-$z$ interim posteriors are overplotted in solid 
lines, with a dotted line indicating zero probability.  Bottom panel: Various 
estimators of $\ln[n(z)]$, the interim prior, and the true $\ln[n(z)]$ as a 
continuous function and under a binned parametrization.}
		\label{fig:featured}
	\end{center}
\end{figure}

@@

In the following test cases, we vary the properties of the mock photo-$z$ 
likelihoods in an effort to emulate known systematics in photo-$z$ estimation.  
These tests vary Step \ref{itm:scatter} of Sec. \ref{sec:mockdata}.

@@

\includegraphics[width=0.5\textwidth]{fig/high_scatter/scatter.png}\\

\includegraphics[width=0.5\textwidth]{fig/high_scatter/estimators.png}		
		\caption{[This would be a lot more compelling with more 
galaxies.  Also, the weird edge effects in the top panel are real, because the 
point estimator is the MAP, not the center of the Gaussian likelihood, and 
there's no requirement that the mean of the likelihood be within the true 
redshift range.]  Top panel: The traditional MAP reduction of a photo-$z$ PDF 
against the true redshifts with a few rescaled photo-$z$ interim posteriors are 
overplotted in solid lines, with a dotted line indicating zero probability.  
Bottom panel: Various estimators of $\ln[n(z)]$, the interim prior, and the 
true $\ln[n(z)]$ as a continuous function and under a binned parametrization.}
		\label{fig:intscat}
	\end{center}
\end{figure}

@@

\includegraphics[width=0.5\textwidth]{fig/template_outliers/scatter.png}\\

\includegraphics[width=0.5\textwidth]{fig/template_outliers/estimators.png}

		\caption{[]  Top panel: The traditional MAP reduction of a 
photo-$z$ PDF against the true redshifts with a few rescaled photo-$z$ interim 
posteriors are overplotted in solid lines, with a dotted line indicating zero 
probability.  Bottom panel: Various estimators of $\ln[n(z)]$, the interim 
prior, and the true $\ln[n(z)]$ as a continuous function and under a binned 
parametrization.}
		\label{fig:tempcatout}
	\end{center}
\end{figure}

@@

Existing $n(z)$ estimation routines will always produce a biased estimator when 
the interim prior is not equal to the true $n(z)$.  We demonstrate here that 
regardless of the appropriateness of the interim prior as an approximation to 
the true $n(z)$, \chippr is not affected by the choice of the interim prior so 
long as it has nontrivial coverage in the space of redshift.  These tests 
modify Step \ref{itm:interim} of Sec. \ref{sec:mockdata}.
